Treatment planning for HDR Brachytherapy

### 2015-03-28 Paper Seminar/classification.tex
cleared up Elmos mess, including the algo and the tables

\subsection{Parameters and Influences}
In table \ref{tbl:classification_parameters}, the various parameters measured in order to compare are displayed. Further on, their influence in the norm is shown. Additionally, in table \ref{tbl:classification_type_weights}, the weighted influence of the five different body types are presented.
\begin{table}
\centering
\caption{Parameters and Influences in classification}
\begin{tabular}[htbp]{l | c | r}
\textbf{Parameter} & \textbf{Influence Type} & \textbf{Weight} \\
volume size  & relative & 0.1\\
volume center & relative & 0.2 \\
distance tumor-center & absolute & 0.2\\
closest distance & absolute & 0.5
\end{tabular}
\label{tbl:classification_parameters}
\end{table}

@@

\begin{table}
\centering
\caption{Influences of Body Types}
\begin{tabular}[htbp]{c | c | c | c | c}
\textbf{normal} & \textbf{spine} & \textbf{liver} & \textbf{pancreas} & \textbf{tumor} \\
1 & 5 & 0.5 & 5 & 3
\end{tabular}
\label{tbl:classification_type_weights}
\end{table}

@@

\begin{algorithm}[H]
\label{alg:classification}
\ForAll{voxels in body}
	count body_type \;
	sum up coordinates \;
	\If{body_type == tumor}
		store coordinate for later usage \;
	\EndIf
\EndFor
volumeCenter = coordinates / body_type \;
centerDistance = euclid_norm (tumorCenter, volumeCenter) \;
\ForAll{voxels in body}
	\ForAll{voxels in tumor stored}
		calculated distance (voxel, tumor) \;
		\If{distance $\textless$ closestDistance}
			update closestDistance \;
		\EndIf
	\EndFor
\EndFor
\caption{Measurement algorithm in pseudo code}
\end{algorithm}

>>>>

\subsection{Parameters and Influences}
In table \ref{tbl:classification_parameters}, the various parameters measured in order to compare are displayed. Further on, their influence in the norm is shown. Additionally, in table \ref{tbl:classification_type_weights}, the weighted influence of the five different body types are presented.
\begin{table}
\centering
\caption{Parameters and Influences in classification}
\begin{tabular}[htbp]{l | c | c}
\textbf{Parameter} & \textbf{Influence Type} & \textbf{Weight} \\ \hline
volume size  & relative & 0.1\\ \hline
volume center & relative & 0.2 \\ \hline
distance tumor-center & absolute & 0.2\\ \hline
closest distance & absolute & 0.5
\end{tabular}
\label{tbl:classification_parameters}
\end{table}

@@

\begin{table}
\centering
\caption{Influences of Body Types}
\begin{tabular}[htbp]{c | c | c | c | c}
\textbf{normal} & \textbf{spine} & \textbf{liver} & \textbf{pancreas} & \textbf{tumor} \\ \hline
1 & 5 & 0.5 & 5 & 3
\end{tabular}
\label{tbl:classification_type_weights}
\end{table}

@@

\begin{algorithm}[H]
\label{alg:classification}
\ForAll{$voxels\ in\ body$}{
	$count\ body\_type;$ \\
	$sum\ up\ coordinates;$\\
	\If{$body\_type == tumor$}{
		$store\ coordinate\ for\ later\ usage;$
	}
}
$volumeCenter = coordinates / body\_type;$ \\
$centerDistance = euclid\_norm (tumorCenter, volumeCenter);$ \\
\ForAll{$voxels\ in\ body$}{
	\ForAll{$voxels\ stored\ in\ tumor$}{
		$calculated\ distance (voxel, tumor);$\\
		\If{distance $\textless$ closestDistance}{
			$update\ closestDistance;$
		}
	}
}
\caption{Measurement algorithm in pseudo code}
\end{algorithm}
